### 2016-03-17 section/3_redundancy.tex
finish revision before section 5

\subsubsection{Fix strategy recommendation}
\label{sec:redundant_fix}
As discussed in Section \ref{sec:tax_study}, extra analysis is needed to
decide whether batching or memoization should be suggested to fix a 
loop that conducts redundant computation.

For cross-iteration redundancy, batching is often used for
I/O operations.
Therefore, we treat I/O related redundancy separately.
When the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, we report this
as I/O related redundancy problem and suggest batching as a potential fix
strategy.

@@

>>>>

\subsubsection{Fix strategy recommendation}
\label{sec:redundant_fix}
\Tool suggests how to fix an inefficient loop to developers.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there is often only one or two natural fix 
strategies for each sub-category of root causes.

Once a loop is identified as \emph{resultless}, \Tool will suggest
the loop to be completely deleted, in case of 0$^*$ resultless, or
conditionally skipped, in case of [0$|$1]*; \Tool will suggest a 
data-structure change in case of 0*1? loops.

When a loop is identified as \emph{redundant}, \Tool conducts
extra analysis to
decide whether batching or memoization should be suggested to fix the
redundancy problem.

For cross-iteration redundancy, \Tool suggests batching if the
redundancy is related to I/O operations and suggests memoization otherwise.
Specifically, 
when the only side effect of a loop is I/O operations
and the same statement(s) is executed in every loop iteration, \Tool reports 
this
as an I/O related redundancy problem and suggests batching as a potential fix
strategy. Otherwise, \Tool suggests memoization.

@@

In addition to the above high-level fix strategies, \Tool can also provide some 
detailed information to help developers design the patch.
For example, in case of memoization fix strategy,
since \Tool knows what exactly are the memory reads that return the same values
again and again, it can help decide what to memoize; in case of
I/O-related batching, \Tool points out the exact I/O operations that should
be considered batching; and so on. 
Generating the exact patch is out of the scope of \Tool.

### 2016-03-17 section/evaltax.tex
trying to make taxonomy presentation natural
finish revision before section 5

\input section/tab_root

\input section/tab_appbug

We quantitatively 
assess the coverage, actionability, and generality of our taxonomy presented
in Section \ref{sec:study} using
a set of
real-world inefficient loop problems collected by previous work
\cite{SongOOPSLA2014,PerfBug}.

@@

\paragraph{Actionability}
As demonstrated in Table \ref{tab:root}, 
the root-cause categories in our taxonomy are well correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultless loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
In fact, as we will discuss later, simple analysis can tell whether 
memoization or batching should be used to fix a redundant loop.
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

@@

\subsection{Caveats} 
Just as previous empirical study work, 
our empirical study above needs to be interpreted with our methodology in mind. 
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are still uncovered cases, like distributed systems, 
and scientific computation.

>>>>

\input section/tab_appbug
\input section/tab_root

The root-cause taxonomy presented in Section \ref{sec:study} is the foundation
of \Tool. In this section,
we quantitatively 
assess the coverage, actionability, and generality of our taxonomy using
a set of
real-world inefficient loop problems collected by previous work
\cite{SongOOPSLA2014,PerfBug}.

@@

\paragraph{Actionability}
As demonstrated in Table \ref{tab:root}, 
the root-cause categories in our taxonomy are well correlated with
fix strategies.
This indicates that our taxonomy is actionable --- once the root cause
is identified, developers roughly know how to fix the problem.
For example, 
almost all 0*1? resultless loops are fixed by data-structure changes;
all [0$|$1]* resultless loops are
fixed by conditionally skipping the loop;
almost all redundant loops are fixed either by 
memoization or batching. 
The only problem is that there are no silver bullets for fixing 1* loops.
%all inefficient loops with xx root cause are fixed by xxx.
%xxx

@@

\subsection{Caveats} 
We do not intend to overly generalize the evaluation results above.
The performance bugs examined above cover a variety of applications, workload, 
development environments and programming languages. 
However, there are still uncovered cases, like distributed systems, 
and scientific computation.
